Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
Minor aesthetic fixes

In addition to fitness monitors, the market for quantified self sensors has
expanded into areas of personal health. For example, there are sensors for
measuring blood oxygenation~\footnote{SpO2 Blood Oxygenation sensor: \url{http://ispo2.com}},
Heart Rate Variability and Respiratory Rate~\footnote{Zensorium Tinke, heart and respiratory rate sensor: \url{http://www.zensorium.com/tinke/}} and
Temperature and Galvanic Skin Response~\footnote{BodyMedia Core 2, temperature and GSR sensor: \url{http://www.bodymedia.com}}.
There is even a wireless fork that informs you how long you spent eating~\footnote{HapiLabs HapiFork: \url{http://hapilabs.com/products-hapifork.asp}}.

>>>>

In addition to fitness monitors, the market for quantified self sensors has
expanded into areas of personal health. For example, there are sensors for
measuring blood oxygenation\footnote{SpO2 Blood Oxygenation sensor: \url{http://ispo2.com}},
Heart Rate Variability and Respiratory Rate\footnote{Zensorium Tinke, heart and respiratory rate sensor: \newline \indent \indent \indent \url{http://www.zensorium.com/tinke/}} and
Temperature and Galvanic Skin Response\footnote{BodyMedia Core 2, temperature and GSR sensor: \newline \indent \indent \indent  \url{http://www.bodymedia.com}}.
The diet aspect of weight loss is also covered, by products such as a wireless fork that informs you how long you spent eating\footnote{HapiLabs HapiFork: \newline \indent \indent \indent  \url{http://hapilabs.com/products-hapifork.asp}}.
